Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Cambios a la Intro para darle más coherencia
Creo que ahora está mejor enlazado todo.

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Companies and particularly their Chief Security Officers (CSOs)
want to ensure that their Security Policies are followed, but this
becomes a difficult goal to achieve at the point employees are able to use, or bring,
their personal devices at work, in a practice that has been named ``Bring Your
Own Device'' (BYOD). % <- Problem
Since this BYOD philosophy is being adopted by many companies
everyday, a number of solutions have appeared in the market so that it
can be implemented in a secure way and comply with the Security Policies
mentioned above. In this paper we present an overview of BYOD security
solutions along a novel, adaptive and open source system named
MUSES (Multiplatform Usable Endpoint Security), able 
to securely manage BYOD environments. % <- Solution
MUSES has been developed to cope with security issues with regard to
enterprise security policies, but as a user-centric tool. It considers
users' behaviour in order to adapt, improve, or even increase the
defined set of security rules. To do this, the system applies Machine
Learning and Computational Intelligence techniques, being also able to
predict future security incidences produced by these users. % <-
                                % Solution, details. 
The MUSES framework, which has released its first prototype in early 2015, is
compared with the most relevant 
solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work
\end{abstract}

%FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD

@@

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
dev\-ice\--in\-de\-pen\-dent end-to-end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
in order to deal with potential security incidents that users might cause in the future. 
Then the system reacts, in a non-intrusive way, to the potentially
dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
any time. The MUSES system has also been tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype. As there was no available test data, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented at \cite{mora14:urls}. % [Pedro] ¿ese "could be" se refiere a verbo en pasado? en ese caso, quizás usar "... was presented at..." % Gracias again
In this paper, once the first MUSES prototype has been released and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them with other existing tools in the market. % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...

@@

% [Pedro] en este punto se puede comentar lo que se va a presentar en el trabajo introduciendo directamente con "This work presents..." o "This paper presents..." (yo quitaría el "But first,"
% Totalmente de acuerdo, cambiado.
This work presents a brief overview of the main existing solutions in the BYOD environment. Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES. % Perfecto, cambiado.
 includes.

@@

\section{Preliminary concepts and background about enterprise security}
\label{sec:preliminaryconcepts}

@@

However, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES. The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Companies and particularly their Chief Security Officers (CSOs)
want to ensure that their Security Policies are followed, but this
becomes a difficult goal to achieve at the point employees are able to use, or bring,
their personal devices at work, in a practice that has been named ``Bring Your
Own Device'' (BYOD). % <- Problem
Since this BYOD philosophy is being adopted by many companies
everyday, a number of solutions have appeared in the market so that it
can be implemented in a secure way and comply with the Security Policies
mentioned above. In this paper we present an overview of BYOD security
solutions along with a novel, adaptive and open source system named
MUSES (Multiplatform Usable Endpoint Security), able 
to securely manage BYOD environments. % <- Solution
MUSES has been developed to cope with security issues with regard to
enterprise security policies, but as a user-centric tool. It considers
users' behaviour in order to adapt, improve, and even increase the
defined set of security rules. To do this, the system applies Machine
Learning and Computational Intelligence techniques, being also able to
predict future security incidences produced by these users. % <-
                                % Solution, details. 
The MUSES framework, which has released its first prototype in early 2015, is
compared with the most relevant 
solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work
\end{abstract}

%FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD
% Antonio - bueno, ya existe. :)

@@

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
dev\-ice\--in\-de\-pen\-dent end-to-end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
in order to deal with potential security incidents that users might cause in the future. 
Then the system reacts, in a non-intrusive way, to the potentially
dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
any time.

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, mainly Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}.

@@

The general ideas behind MUSES were already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
published. Also, an additional work on applying data mining and machine learning techniques was conducted in \cite{mora14:urls}. It presented a study over a dataset similar to those that MUSES will manage, but not the same, since the prototype of MUSES had not still been released.
Thus, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented in that work. % [Pedro] ¿ese "could be" se refiere a verbo en pasado? en ese caso, quizás usar "... was presented at..." % Gracias again

% Antonio- muevo esta frase a un sitio más adecuado
The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we have now a clearer idea of its capabilities. 
Thus, in this paper we present an overview of the main existing solutions in the BYOD environment. Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES. % Perfecto, cambiado.
 includes.

@@

% Antonio - Yo separaría esta sección en dos: Preliminary concepts y SOA. Así se suele hacer y así podemos destacar en la respuestas lo de la nueva sección con el SOA. Eso sí, en ese caso debería ser mayor y mejor. ¿Qué opináis?
\section{Preliminary concepts and background about enterprise security}
\label{sec:preliminaryconcepts}

@@

As stated, MUSES has been recently tested in an actual company with satisfactory results according to the users' and to the evaluators of the trials.
% Antonio - lo del trabajo futuro mejor decirlo al final. En la intro no se suele poner a no ser que quieras aclarar que este trabajo no va de esto. Pero eso suele verse como algo negativo. Los revisores te pueden decir que por qué no has hecho ese análisis si ya tienes los datos...
However, the analysis of all data from these tests, and conclusions, will be addressed in future works.

There is also room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES. The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.
